---
title: "Aides Drug"
author: "Yasheika Pink"
date: "May 2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
triUmp <-read.csv(file="triUmpsal.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (triUmpsal) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. Analyze the difference in pharmaseutical effect based on gender. How the the drug metabolizes based on drug use, causing an adverse reaction to the chemistry of the new preventive aides drug. And will the drug have the same effect or decrease response to any person of non-traditional sexual orientation. And psycosocial status. To see whether therapeutic vaccination is safe and can affect how the body responds to HIV infection.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
because all vaiables are categorical, we use a bar chart for the graphical description, a cross tabulation for the numerical summary and a chi-squared, test and Fisher exact test for inference 

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

$H_0$ : the vaccine has no effect on whether one contracts Aids or not
$H_0$  the vaccine has an effect on whether one contracts Aids or not

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected + treatment,data=triUmp, type = "percent")
            
```
This graph shows that the drug may be effective against aquiring Aids, and the placebo group is a 50/50 effectiveness.


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

The rationale for testing the study vaccine regimen in this subject population is because these individuals may have a relatively preserved immune function, which could be augmented by therapeutic vaccination. Noticed that many psychological, social and behavioral factors tend to influence the efficacy of medication and the overall therapeutic outcome for these individuals compared with those who are less suggestible.

```{r}
table1 <- xtabs(~infected + treatment, data=triUmp )
rowPerc(table1)
colPerc(table1)
```

description of what the table says


```{r}
table1 <- xtabs(~infected + treatment, data=triUmp)
rowPerc(table1)
colPerc(table1)
```
This table shows that among those who contracted Aids, .. 

### Inferential results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


### Question # 2
$H_0$ : the vaccine has no effect on whether one in the LGBTQ community contracts Aids or not
$H_A$  the vaccine has an effect on whether one contracts Aids or not

### graphic results
```{r}

LGBTQdata = filter(triUmp, LGBTQ== 'gay')
barchartGC(~infected + treatment,data=LGBTQdata, type = "percent")
            
```

### numerical summary

```{r}

table1 <- xtabs(~infected + treatment, data=LGBTQdata)
rowPerc(table1)
colPerc(table1)
```

### inferential

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
the p-values show that 

### question #3: does the drug have an effec on whether or not women contract Aids?

$H_0$ : the vaccine has no effect on whether a female contracts Aids or not
$H_A$  the vaccine has an effect on whether a female contracts Aids or not

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
FemalesData = filter(triUmp, gender == 'F')
barchartGC(~infected + treatment,data=FemalesData, type = "percent")
            
```
This graph shows that the drug may be effective aquiring Aids, and the placebo group is a 50/50 effectiveness.


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

The rationale for testing the study vaccine regimen in this subject population is because these individuals may have a relatively preserved immune function, which could be augmented by therapeutic vaccination. Noticed that many psychological, social and behavioral factors tend to influence the efficacy of medication and the overall therapeutic outcome for these individuals compared with those who are less suggestible.

```{r}
table1 <- xtabs(~infected + treatment, data=FemalesData )
rowPerc(table1)
colPerc(table1)
```

description of what the table says


```{r}
table1 <- xtabs(~infected + treatment, data=FemalesData)
rowPerc(table1)
colPerc(table1)
```
This table shows that among those who contracted Aids, .. 

### Inferential results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
